Text as Policy: \\ Measuring Policy Similarity through Bill Text Reuse

### 2016-09-21 manuscript/main.tex
update to paper

\section{Introduction} The diffusion of public policy has been a central focus in political science research since at least \citet{walker1969}. Research on public policy adoption and diffusion has conventionally relied on modestly-sized, hand-coded datasets that record when a set of jurisdictions adopt one or a handful of similar policies \citep{boehmke2012}. In this paper we draw upon a voluminous and comprehensive source of data with which to measure the consideration and adoption of similar policies -- the text of legislation considered in US state legislatures. We take an automated, text-as-data, approach to the analysis of bill text. This vastly increases the volume of data that can be included in policy adoption research.

@@

\section{Policy Similarity in US State Legislation}
% What we will provide through the application of the SW algorithm?
Through the application of the SW algorithm to US state legislation, we will provide a quantitative measure of policy similarity between bill sections. We follow \citet{wilkerson2015tracing} in focusing on sections, as bills can contain many separate policy proposals. The similarity measures between sections that we identify can be aggregated up to the bill, legislator or state levels. The measures we provide can be used to test hypotheses regarding, among other topics, public policy diffusion, legislative politics, political parties, and interest groups.

@@

All bills are split up into sections in order to be able to detect all alignments between two bills. Because the SW algorithm only returns the one best alignment between two sequences, relevant information might be lost when considering every bill as one large sequence of words. 
The SW algorithm is computationally demanding and an exhaustive comparison of all possible bill-section-pairs is not feasible (with $500,000$ bills, assuming each bill consists on average of four sections this would amount to about $2 * 10^{12}$ comparisons). \citet{wilkerson2015tracing} encountered the same problem and excluded bills that don't have at least five matching 10-grams. Since this implies considerable exact character matches, we see this as a too restrictive for our application. Because the text we are using originates in 50 different legislatures, exact character matches might obfuscate valuable text reuse just because of small formatting changes, changes of state names, etc. 
Instead we choose to rely on a procedure that is based on finding bills with
similar language. We store all available bills in an Elastic Search database.
Elastic search is an open source web search engine which is designed to find
document that match a search query \citep{gormley2015elasticsearch}. We utilize
the `more like this' query, which is designed to find documents that are similar
to a given document. It works in the following way: From the focus document, the
$k$ $n$-grams with the highest tf-idf scores are selected and transformed into a
search vector that is representative of the query document. Then, for each
document in the collection, a variation of the cosine similarity is calculated
and the $m$ bills with the highest scores are selected for further analysis. For
this analysis we set $k$ to 25, $n$ to 5 and $m$ to 1000\footnote{For
details on the exact algorithm we refer the reader to the elastic search
documentation (\url{http://sunlightfoundation.com/} as well as the lucene engine
documentation
(\url{https://lucene.apache.org/core/4_9_0/core/org/apache/lucene/search/similarities/TFIDFSimilarity.html}).
In order to account for the possibility of selection bias being introduced to
our analyses through the cap of 1000 similar bills, we analyzed the results with
different numbers of pre-selected bills. We find that this parameter, when set
to a sufficiently high value, does not lead to such bias because the set of
potentially relevant bills is always much smaller than 1000.}

@@

Once the candidate sections are selected, the alignments are calculated for all possible bill-section-dyads, section-pairs from the same bill and section pairs from the same state are excluded. We exclude same-state comparisons in the current analysis since our validation exercises are focused on cross-state comparisons. We refer to the two sections involved in each alignment process as `left' and `right' sections. The algorithm returns parts of the left and right section that are determined to be aligned as well as a score. We refer to these three pieces of information as an alignment.

>>>>

\section{Introduction}

The diffusion of public policy has been a central focus in political science research since at least \citet{walker1969}. Research on public policy adoption and diffusion has conventionally relied on modestly-sized, hand-coded datasets that record when a set of jurisdictions adopt one or a handful of similar policies \citep{boehmke2012}. In this paper we draw upon a voluminous and comprehensive source of data with which to measure the consideration and adoption of similar policies -- the text of legislation considered in US state legislatures. We take an automated, text-as-data, approach to the analysis of bill text. This vastly increases the volume of data that can be included in policy adoption research.

@@

\section{Policy Similarity in US State Legislation}
% What we will provide through the application of the SW algorithm?
Through the application of the SW algorithm to US state legislation, we will
provide a quantitative measure of policy similarity between bills. The
similarity measures between bills  that we identify can be aggregated up to the legislator or state levels. The measures we provide can be used to test hypotheses regarding, among other topics, public policy diffusion, legislative politics, political parties, and interest groups.

@@

The SW algorithm is computationally demanding and an exhaustive comparison of
all possible bill-pairs is not feasible (with $500,000$ bills this would amount
to about $124 * 10^9$ bill pairs). \citet{wilkerson2015tracing} encountered the same problem and excluded bills that don't have at least five matching 10-grams. Since this implies considerable exact character matches, we see this as a too restrictive for our application. Because the text we are using originates in 50 different legislatures, exact character matches might obfuscate valuable text reuse just because of small formatting changes, changes of state names, etc. 
Instead we choose to rely on a procedure that is based on finding bills with
similar language. We store all available bills in an Elastic Search database.
Elastic search is an open source web search engine which is designed to find
document that match a search query \citep{gormley2015elasticsearch}. We utilize
the `more like this' query, which is designed to find documents that are similar
to a given document. It works in the following way: From the focus document, the
$k$ $n$-grams with the highest tf-idf scores are selected and transformed into a
search vector that is representative of the query document. Then, for each
document in the collection, a variation of the cosine similarity is calculated
and the $m$ bills with the highest scores are selected for further analysis. For
this analysis we set $k$ to 25, $n$ to 5 and $m$ to 1000\footnote{For
details on the exact algorithm we refer the reader to the elastic search
documentation (\url{http://sunlightfoundation.com/} as well as the lucene engine
documentation
(\url{https://lucene.apache.org/core/4_9_0/core/org/apache/lucene/search/similarities/TFIDFSimilarity.html}).
In order to account for the possibility of selection bias being introduced to
our analyses through the cap of 1000 similar bills, we analyzed the results with
different numbers of pre-selected bills. We find that this parameter, when set
to a sufficiently high value, does not lead to such bias because the set of
potentially relevant bills is always much smaller than 1000.}

@@

Once the candidate bills are selected, the alignments are calculated for all
possible bill-dyads, bill pairs from the same state are available but excluded
for the analyses below. We exclude same-state comparisons in the current analysis since our validation exercises are focused on cross-state comparisons. We refer to the two sections involved in each alignment process as `left' and `right' sections. The algorithm returns parts of the left and right section that are determined to be aligned as well as a score. We refer to these three pieces of information as an alignment.
